Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-06-02 performance_comparison.tex
[MM] intro to saturation
still no nice name for the quantity

From the first panel, it can be observed that all configurations maintain a lower mean value of the longitudinal speed compared to the reference trajectory, resulting in an increased sector time. Specifically, the configuration with the robustified TLC increases the sector time by 1.66\%, while the configuration with the robustified FLC and with both TLC and FLC robustified increase the sector time by a 0.79\% and 2.57\%, respectively.
The two configurations incorporating the robustified track limit constraint (blue and green lines) exhibit, as expected, a significantly altered CoM trajectory. This behavior explains the higher longitudinal speed observed around $\al = 0.71$, which is followed by a sharp reduction.

@@

@@

>>>>

From the first panel, it can be observed that all configurations maintain a lower mean value of the longitudinal speed compared to the reference trajectory, resulting in an increased sector time. Specifically, the configuration with the robustified TLC increases the sector time by 1.66\%, while the configuration with the robustified FLC and with both TLC and FLC robustified increase the sector time by 0.79\% and 2.57\%, respectively.
The two configurations incorporating the robustified track limit constraint (blue and green lines) exhibit, as expected, a significantly altered CoM trajectory. This behavior explains the higher longitudinal speed observed around $\al = 0.71$, which is followed by a sharp reduction.

@@

After analyzing the variations of four key signals with respect to the nominal solution, we now turn our attention to the evaluation of axle saturation, which provides insight into how close each configuration operates to the tire grip limits.
Figure~\ref{fig:ol_saturation} presents the quantity $\left[ \left( \frac{X_j(\bx,\bu)}{\mu_{x,j}} \right)^2+ \left( \frac{Y_j(\bx,\bu)}{\mu_{y,j}}\right)^2\right]\frac{1}{Z_j^2(\bx,\bu)}$, where $j=1$ refers to the front axle (first panel) and $j=2$ the rear axle (second panel), plotted for the three previously introduced configurations (color-coded as before) and for the nominal solution (black dashed line). This quantity indicates how close each configuration operates to the friction limit; it equals 1 when the point $\left(X_j, Y_j\right)$ lies exactly on the friction ellipse defined by $Z_j$.

@@

As expected, the two configurations with the robustified friction limit constraint (red and blue lines) never reach a value of 1, due to the presence of the back-off term, which enforces a safety margin from the friction limit.
